### 2018-12-17 README.Rmd
remove references to aw_ data

data(ar_stl_asthma, package = "areal")
asthma <- aw_stl_asthma

data(ar_stl_race, package = "areal")
race <- aw_stl_race

data(ar_stl_wards, package = "areal")
wards <- aw_stl_wards
```

>>>>

data(ar_stl_asthma, package = "areal")
asthma <- ar_stl_asthma

data(ar_stl_race, package = "areal")
race <- ar_stl_race

data(ar_stl_wards, package = "areal")
wards <- ar_stl_wards
```
